Hyperspectral tree defoliation modeling with a focus on feature-selection and model interpretation

### 2019-06-23 code/98-paper/journal/manuscript.tex
restructure methods, list benchmark matrix

\begin{itemize}
	\item The raw hyperspectal band information (HR): No feature engineering
	\item Vegetation Indices (\ac{VI}: Expert-based feature engineering
	\item Normalized Ratio Indices (\ac{NRI}): Automated feature-engineering
\end{itemize}

\noindent A spatial block nested cross-validation was chosen to reduce the influence of spatial autocorrelation as much as possible.
Each plot served as one fold within the resampling setup, resulting in four folds total.
For the inner level (hyperparameter tuning), $p - 1$ folds were used (with $p$ being the number of plots). REF SCHRATZ

@@

\noindent The complete study was done using the open-source statistical programming language R \citep{rcoreteam2018}.
The algorithm implementations of the following packages have been used: \textit{xgboost} \citep{chen2016} (\textit{xgboost}), \textit{e1071} \citep{e1071} (Support Vector Machine) and \textit{glmnet} \citep{glmnet} (Ridge Regression).
The filter methods of the following packages were used: \textit{praznik \citep{praznik}}, \textit{FSelectorRcpp} \citep{fselectorrcpp}.
The R package \textit{mlr} \citep{mlr} was used for all modeling related steps.
\textit{drake} was used for structuring the work and ensuring reproducibility.
This study is available as a research compendium on Zenodo (\url{10.5281/zenodo.2635403}).

>>>>

@@

\subsubsection{Algorithms}

\begin{itemize}
	\item The raw hyperspectal band information (HR: No feature engineering)
	\item Vegetation Indices (\ac{VI}: Expert-based feature engineering)
	\item Normalized Ratio Indices (\ac{NRI}: Automated feature-engineering)
\end{itemize}

For the filter methods, the percentage of features was optimized as a hyperparameter.
The number of main components was tuned for the \ac{PCA} based benchmarking experiments.

\noindent A spatial block nested cross-validation was chosen to reduce the influence of spatial autocorrelation as much as possible \citep{schratz2019, sperrorest}.
Each plot served as one fold within the resampling setup, resulting in four folds total.
For the inner level (hyperparameter tuning), $p - 1$ folds were used (with $p$ being the number of plots).

\subsubsection{Summary}

\noindent In total the benchmarking matrix consisted of 120 experiments (3 feature sets, 5 algorithms, 8 feature-selection methods).

\subsection{Research compendium}

\noindent The complete study was done using the open-source statistical programming language R \citep{rcoreteam2018}.
The algorithm implementations of the following packages have been used: \textit{xgboost} \citep{chen2016} (\textit{xgboost}), \textit{kernlab} \citep{kernlab} (Support Vector Machine) and \textit{glmnet} \citep{glmnet} (Ridge Regression).
The filter methods of the following packages were used: \textit{praznik \citep{praznik}}, \textit{FSelectorRcpp} \citep{fselectorrcpp}.
The R package \textit{mlr} \citep{mlr} was used for all modeling related steps.
\textit{drake} was used for structuring the work and ensuring reproducibility.
This study is available as a research compendium on Zenodo (\url{10.5281/zenodo.2635403}).
